Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-04 programlogic.tex
+

\item Physical address points-to, $\pfpointsto\locsf\locsf\qfrac\ppts$

@@

\paragraph{Physical-Memory points-to} Our physical memory points-to relation for a page table entry (e.g. \textsf{PDE} in Figure \ref{fig:physicalpointsto}) abstracts masking -- $|^{52}$ for frame for and $|^{12}$ for offset -- through logical nested maps.  

@@

\pfpointsto\locsf\locsf\qfrac\ppts \stackrel{def}{=} & \nfpointsto{\mask\locsf\ft\generalentry}{\mask\locsf\tw\generalentry}\locsf\qfrac\naddr

>>>>

\item Physical address points-to, $\pfpointsto\locsf\vpts\qfrac\ppts$

@@

\paragraph{Physical-Memory points-to} Our physical memory points-to relation in Figure \ref{fig:physicalpointsto} for a page table entry (e.g. \textsf{PDE} in Figure \ref{fig:pagetables}) abstracts masking -- $|^{52}$ for frame for and $|^{12}$ for offset -- through logical nested maps.  

@@

\pfpointsto\locsf\vpts\qfrac\ppts \stackrel{def}{=} & \nfpointsto{\mask\locsf\ft\generalentry}{\mask\locsf\tw\generalentry}\vpts\qfrac\naddr
